---
output: rmarkdown::github_document
---

# astools

Tools to Work With Autonomous System ('AS') Network and Organization Data

## Description

A collection of utilities for downloading, parsing, reading and analyzing autonomous system ('AS') network and organization data from various internet sources including 'CAIDA' (<https://caida.org>) and 'BGP Routing Table Analysis Reports' <https://bgp.potaroo.net>

## What's Inside The Tin

The following functions are implemented:

- `asnames_current`:	Retrive current 'asnames.txt' from 'bgp.poraroo.net'
- `read_asnames`:	 Retrieve an historical `asnames.txt` from local cache
- `parse_asnames`:	Parse arbitrary 'asnames.txt' downloaded from 'bgp.poraroo.net'
- `parse_asorg2info`:	Parses CAIDA 'asorg2info' Files
- `parse_routeviews`:	Parses Arbitrary RouteViews "Prefix-to-AS" Files
- `as_asntrie`:	Convert a 'routeviews' data frame to a trie
- `routeviews_latest`:	Caches & Returns the latest CAIDA-processed RouteViews "Prefix-to-AS" File

## Installation

```{r eval=FALSE}
devtools::install_github("hrbrmstr/astools")
```

```{r message=FALSE, warning=FALSE, error=FALSE, include=FALSE}
options(width=120)
```

## Usage

```{r message=FALSE, warning=FALSE, error=FALSE}
library(astools)
library(tidyverse)

# current verison
packageVersion("astools")

```

### RouteViews Prefix-to-AS

```{r}
(rv_df <- routeviews_latest())
```

Which can with `iptools::ip_to_asn()`:

```{r}
rv_trie <- as_asntrie(rv_df)

iptools::ip_to_asn(rv_trie, "174.62.167.97")
```

### AS Org-to-Info

```{r}
parse_asorg2info("~/Data/20180703.as-org2info.txt.gz")
```

### AS Names

```{r}
asnames_current()
```

### Combining RouteViews & AS Names

These are now cached so there is no re-downloading.

```{r}
routeviews_latest() %>% 
  left_join(asnames_current())
```
